Formalizing Stack Safety as a Security Property

### 2021-07-09 submission3/main.tex
Test policy descriptions

\sna{I am not sure about the MTTF table. Is it as
  valuable at POPL? Do we need to go into more detail
  about metholodology if we use it?}

%\begin{table}[]
%\centering
%\begin{tabular}{c|c|c}
%  Bug & Property Violated & MTTF (ms) \\
%  \hline
%      {\em LOAD\_NO\_CHECK}  & Confidentiality & 1670 \\
%      {\em STORE\_NO\_CHECK} & Integrity & 638 \\
%      {\em HEADER\_NO\_INIT} & Integrity & 1488 \\
%\end{tabular}
%\vspace*{1em}
%\caption{MTTF for finding bugs in erroneous policy enforcement mechanisms}
%\vspace*{-2em}
%\label{tab:bug-table}
%\end{table}

%The mean-time-to-failure (MTTF) for various bugs can be found in
%Table~\ref{tab:bug-table}. All experiments were run in a desktop
%machine equipped with i7-8700 CPU @ 3.20GHz with 32GB
%RAM.
% \leo{Something like: There is really no baseline to compare this
  %against, but include it here for the future/reasons?}
%
The artificially injected bugs weaken the tag propagation
and checking mechanism.
%
For example, when loading from a stack location, the correct
micro-policy needs to enforce that the tag on the location being read
is $\tagStackDepth{n}$ for some number $n$ and that the tag of the
current $\PCname$ is $\tagPCDepth{n}$ for the same depth $n$. We can relax
that restriction by not checking the depth equality (row {\em
  LOAD\_NO\_CHECK}).
%
Similarly, when storing to a stack location, the correct micro-policy
needs to ensure that the tag on the memory location is either
$\tagNoDepth$ or has again the same depth as the current $\PCname$
tag. Relaxing that constraint causes violations to the integrity
property (row {\em STORE\_NO\_CHECK}).

@@

Observable properties allow us to defer enforcement until a property
violation would become visible. Now we can identify when lazy policies
miss such violations. The Lazy Tagging and Clearing
micro-policy from \citet{DBLP:conf/sp/RoesslerD18} tags each stack slot with the call depth
at which it was written, and enforces that it must be read from the
same depth. However, this allows violations of observable stack safety!
Specifically, a callee might write into the stack and leave tags behind
for a future callee at the same depth to read. This violates confidentiality and,
if the writes were in the caller's frame, integrity. \apt{A more detailed example
  would be great here, and should not take too much space.}
\apt{Mention here that this was found by testing.}

@@

We test {\em Lazy Per-activation Tagging and Clearing}, in which
each activation is tagged uniquely, and find that it obeys stepwise
confidentiality and observational integrity. Our testing catches the
violation in the original {\em Lazy Tagging and Clearing}, as well as
an equivalent to {\em LOAD\_NO\_CHECK}, which now also violates observational
integrity.\apt{Move latter to above.}

>>>>

\begin{table}[]
\centering
\begin{tabular}{c|c|c}
  Bug & Property Violated & MTTF (ms) \\
  \hline
      {\em LOAD\_NO\_CHECK}  & Confidentiality &  \\
      {\em STORE\_NO\_CHECK} & Integrity &  \\
      {\em HEADER\_NO\_INIT} & Integrity &  \\
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous policy enforcement mechanisms}
\vspace*{-2em}
\label{tab:bug-table}
\end{table}

The mean-time-to-failure (MTTF) for various bugs can be found in
Table~\ref{tab:bug-table}. All experiments were run in a desktop
machine equipped with i7-8700 CPU @ 3.20GHz with 32GB
RAM.
% \leo{Something like: There is really no baseline to compare this
  %against, but include it here for the future/reasons?}
%
The artificially injected bugs weaken the tag propagation
and checking mechanism.
%
For example, when loading from a stack location, the correct
micro-policy needs to enforce that the tag on the location being read
is $\tagStackDepth{n}$ for some number $n$ and that the tag of the
current $\PCname$ is $\tagPCDepth{n}$ for the same depth $n$. We can relax
that restriction by not checking the depth equality (row {\em
  LOAD\_NO\_CHECK}).
%
Similarly, when storing to a stack location, the correct micro-policy
needs to ensure that the tag on the memory location is either
$\tagNoDepth$ or has again the same depth as the current $\PCname$
tag. Relaxing that constraint causes violations to the integrity
property (row {\em STORE\_NO\_CHECK}).

@@

Observable properties allow us to defer enforcement until a property
violation would become visible. Now we can identify when lazy policies
miss such violations. The Lazy Tagging and Clearing
micro-policy from \citet{DBLP:conf/sp/RoesslerD18} tags each stack slot with the call depth
at which it was written, and enforces that it must be read from the
same depth. However, this allows violations of observable stack safety!
Our implementation of this policy, {\em PER\_DEPTH\_TAG}, has an error that we find
in testing. If, at depth \(d\), a callee \(A\) writes into its caller's
frame, then returns, and later another callee \(B\) at depth \(d\) reads the same
address and prints it, \(A\) has violated integrity in a way that later becomes visible,
and \(B\) has likewise violated confidentiality!

@@

We test {\em Lazy Per-activation Tagging and Clearing}, in which
each activation is tagged uniquely, and find that it obeys stepwise
confidentiality and observational integrity. To round out our mutations testing 
we also check an equivalent to {\em LOAD\_NO\_CHECK} and a version where
stores succeed but fail to propagate the PC tag, {\em STORE\_NO\_UPDATE}.

\begin{table}[]
\centering
\begin{tabular}{c|c|c|c}
	Bug & Property Violated & MTTF (ms) & Tests \\
  \hline
	{\em PER\_DEPTH\_TAG} & Observational Integrity &  & \\
	{\em LOAD\_NO\_CHECK}  & Observational Integrity &  & \\
	{\em STORE\_NO\_UPDATE} & Observational Integrity &  & \\
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous policy enforcement mechanisms}
\vspace*{-2em}
\label{tab:lazy-bug-table}
\end{table}
